Price of Anarchy for Mean Field Games

### 2018-07-06 PoA.tex
small changes

In the following, we intend to simplify the explicit solutions (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) for the social costs in the LQEMFG and LQEMKV problems. First, consider the quantity $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$. Using equation (\ref{eq:eta_bar_MFG}), we have:
\begin{equation*}
\begin{split}
&\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt\\
=& - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T ((2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \right]\\
\end{split}
\end{equation*}
Then by integration by parts:
\begin{equation*}
\begin{split}
= & - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2-\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2-2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t\dot{\bar{x}}^{MFG}_t dt \\
& + \int_0^T ( (2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s)) (\bar{x}^{MFG}_t)^2 dt \Bigg] \\
\end{split}
\end{equation*}
Then using equation (\ref{eq:x_bar_MFG}):
\begin{equation*}
\begin{split}
= & 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\bar{x}^{MFG}_0)^2 \\
&- \int_0^T  (\bar{b}_1 \bar{\eta}^{MFG}_t -(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
\end{split}
\end{equation*}
Finally, we solve:
\begin{equation*}
\begin{split}
\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\bar{x}^{MFG}_0)^2 \\
&+ \int_0^T  (-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
\end{split}
\end{equation*}
If we denote:
\begin{equation*}
\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},
\end{equation*}
\begin{equation*}
h_{var}: = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T,
\end{equation*}
and use the terminal condition for $\bar{\eta}^{MFG}_T$, then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
\begin{equation}
\begin{split}
SC^{MFG} = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 \bar{x}_0^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
\end{split}
\label{eq:SC_MFG_2}
\end{equation}
Repeating the calculation for $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$ (using equations (\ref{eq:eta_bar_MKV}) and (\ref{eq:x_bar_MKV})), we arrive at:
\begin{equation*}
\begin{split}
\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{1}{c^{MKV}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\bar{x}^{MKV}_0)^2 \\
&+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt \Bigg],
\end{split}
\end{equation*}
Using the terminal condition for $\bar{\eta}^{MKV}_T$, equation (\ref{eq:SC_MKV_1}) can be rewritten as:
\begin{equation}
SC^{MKV} = h_{var} + \frac{1}{2} \bar{\eta}^{MKV}_0 \bar{x}_0^2.
\label{eq:SC_MKV_2}
\end{equation}

@@

\begin{proposition}
	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by
	\begin{equation*}
		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
	\end{equation*}
\label{prop:diff_SC}
\end{proposition}
\begin{proof}
	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the Riccati equations (\ref{eq:eta_bar_MFG}) and (\ref{eq:eta_bar_MKV}), respectively, are well defined under assumption (\ref{eq:assumptions}) (see Appendix \ref{appendix_solving_fbsdes}). We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following first-order differential equation:
	\begin{equation*}
		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t,
		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV}
	\end{equation*}
	with coefficients:
	\begin{equation*}
	\left\{
		\begin{array}{rcl}
			\gamma_t &=& \displaystyle -2 b_1 - 2\bar{b}_1 + \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \left(\lambda \bar{\eta}_t^{MFG} + \bar{\eta}_t^{MKV} \right),\\
			\beta_t &=& \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q + \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)).
		\end{array}
	\right.
	\end{equation*} 
	Since $q_T + \bar{q}_T(1-s_T) = \bar{\eta}_T^{MFG}$, $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}) that:
	\begin{equation*}
		\begin{split}
			& SC^{MFG} - SC^{MKV}\\
			=& \frac{1}{2} \left[ \Delta\bar{\eta}_0 \bar{x}_0^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
			=& \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
			=& \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2\left(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}\right) - \gamma_t\right] dt\\
			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt,
		\end{split}
	\end{equation*}
	where we use equation (\ref{eq:x_bar_MFG}) for the fourth equality.

@@

Therefore, under assumption (\ref{eq:assumptions}), the price of anarchy for the LQ model is given by 
\begin{equation}
PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + \bar{\eta}_0^{MKV} \bar{x}_0^2}.
\label{eq:PoA_LQ}
\end{equation}\\

@@

	When $r \to \infty$ we have
	\begin{equation*}
		\lambda \to \lambda^{\infty,r} := \frac{b_2}{b_2 + \bar{b}_2}
	\end{equation*}
	and
	\begin{equation*}
		B \to 0,\ B^\eta \to 0,\ C^u \to C_u^{\infty,r} := \lambda^{\infty,r}(q + \bar{q}(1-s)),\ D^{u} \to D_u^{\infty,r} := \lambda^{\infty,r}(q_T+ \bar{q}_T(1-s_T)).
	\end{equation*}
	Since assumption (\ref{eq:assumptions}) holds for arbitrary large $r$, we can deduce that the solution $u_t$ of equation (\ref{eq:riccati_ut}) tends to a limiting function $u^{\infty,r}_t$ which is the solution of a first-order differential equation (see Appendix \ref{appendix_solving_fbsdes}). The limiting solution $u_t^{\infty,r}$ is given by:
	\begin{equation*}
	\begin{split}
	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u},\\
	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t),
	\end{split}
	\end{equation*}
	which is bounded for $t \in [0,T]$.
	Similarly, we have the bounded limiting solutions over $[0,T]$:
	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}.$$
	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have 
	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t
	$$
	which are also bounded over $t\in[0,T]$.
	Hence, by the bounded convergence theorem we have
	\begin{equation*}
		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty.
	\end{equation*}
	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$ and therefore,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 \bar{x}_0^2 \  >0.
	\end{equation*}
	Thus, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we deduce $\displaystyle \lim_{r \to \infty} PoA = 1$.

@@

\begin{proof}
    First, we consider $b_2 \to 0$. We assume here $\bar{b}_2 \neq 0$. Otherwise, if $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. 
    For $\bar{b}_2 \neq 0$, we have $\lambda \to 0 $ and
	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$

	By taking the limit $b_2 \to 0$, we have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
	$$u_t \xrightarrow[b_2 \to 0 ]{} 0, \quad \forall t \in [0,T].$$
	This implies that $\bar{x}_t^{MFG} \to \bar{x}_0 \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.

	Since $B^{0,b_2} \neq0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$. Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get
	\begin{equation*}
	\begin{split}
	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }\\
	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t)
	\end{split}
	\end{equation*}
	which are bounded over $[0,T]$. Thus, the limiting variance function $ v_t \to  v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for $t>0$ and $v^{0,b_2}_t$ is bounded.
	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
	\begin{equation*}
	\begin{split}
	    \lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{0,b_2,MFG})^2 dt,\\
	    \lim_{b_2 \to 0} \Delta SC &>0, \\
	    \lim_{b_2 \to 0} \Delta SC &< \infty ,
	\end{split}
	\end{equation*}
	and using the fact that $w^{0,b_2}_t\not \equiv 0$  and using equation (\ref{eq:SC_MKV_2}), $ \lim_{b_2\to 0} SC^{MKV} >0 $.
	Therefore, combined with equation (\ref{eq:PoA_LQ}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$

>>>>

In the following, we intend to simplify the explicit solutions (\ref{eq:SC_MFG_1}) and (\ref{eq:SC_MKV_1}) for the social costs in the LQEMFG and LQEMKV problems. First, consider the quantity $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$. Using equation (\ref{eq:eta_bar_MFG}), we have:
\begin{equation*}
\begin{split}
&\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt\\
=& - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \left[ \int_0^T \dot{\bar{\eta}}^{MFG}_t (\bar{x}^{MFG}_t)^2 dt +  \int_0^T ((2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \right]\\
\end{split}
\end{equation*}
Then by integration by parts:
\begin{equation*}
\begin{split}
= & - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T(\bar{x}^{MFG}_T)^2-\bar{\eta}^{MFG}_0(\bar{x}^{MFG}_0)^2-2\int_0^T\bar{\eta}^{MFG}_t\bar{x}^{MFG}_t\dot{\bar{x}}^{MFG}_t dt \\
& + \int_0^T ( (2b_1 + \bar{b}_1) \bar{\eta}^{MFG}_t +(q+\bar{q}(1-s)) (\bar{x}^{MFG}_t)^2 dt \Bigg] \\
\end{split}
\end{equation*}
Then using equation (\ref{eq:x_bar_MFG}):
\begin{equation*}
\begin{split}
= & 2 \int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2dt  - \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} \Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
&- \int_0^T  (\bar{b}_1 \bar{\eta}^{MFG}_t -(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
\end{split}
\end{equation*}
Finally, we solve:
\begin{equation*}
\begin{split}
\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt= \frac{1}{c^{MFG}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MFG}_T (\bar{x}^{MFG}_T)^2 - \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 \\
&+ \int_0^T  (-\bar{b}_1 \bar{\eta}^{MFG}_t+(q+\bar{q}(1-s))) (\bar{x}^{MFG}_t)^2 dt \Bigg].
\end{split}
\end{equation*}
If we denote:
\begin{equation*}
\lambda := \frac{c^{MFG}}{c^{MKV}} = \frac{b_2}{b_2 + \bar{b}_2}\cdot \frac{ r + \bar{r}(1-\bar{s})^2 }{r + \bar{r}(1-\bar{s})},
\end{equation*}
\begin{equation*}
h_{var}: = \frac{1}{2}\int_0^T (q+\bar{q}+(r+\bar{r})(a\eta_t)^2)v_tdt + \frac{1}{2}(q_T+\bar{q}_T)v_T,
\end{equation*}
and use the terminal condition for $\bar{\eta}^{MFG}_T$, then equation (\ref{eq:SC_MFG_1}) can be rewritten as:
\begin{equation}
\begin{split}
SC^{MFG} = & h_{var} +  \frac{1}{2} \int_0^T \left[ \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q+ \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)) \right] (\bar{x}_t^{MFG})^2 dt, \\
& + \frac{1}{2} \lambda \left( \bar{\eta}^{MFG}_0 (\mathbb{E}(\xi))^2 - (q_T+\bar{q}_T(1-s_T)) (\bar{x}_T^{MFG})^2 \right) + \frac{1}{2} (q_T+\bar{q}_T(1-s_T)^2)(\bar{x}_T^{MFG})^2.
\end{split}
\label{eq:SC_MFG_2}
\end{equation}
Repeating the calculation for $\int_0^T (\bar{\eta}^{MFG}_t)^2 (\bar{x}^{MFG}_t)^2 dt$ (using equations (\ref{eq:eta_bar_MKV}) and (\ref{eq:x_bar_MKV})), we arrive at:
\begin{equation*}
\begin{split}
\int_0^T (\bar{\eta}^{MKV}_t)^2 (\bar{x}^{MKV}_t)^2 dt=\frac{1}{c^{MKV}(b_2 + \bar{b}_2)} &\Bigg[ \bar{\eta}^{MKV}_T (\bar{x}^{MKV}_T)^2 - \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2 \\
&+ \int_0^T (q+\bar{q}(1-s)^2) (\bar{x}^{MKV}_t)^2 dt \Bigg],
\end{split}
\end{equation*}
Using the terminal condition for $\bar{\eta}^{MKV}_T$, equation (\ref{eq:SC_MKV_1}) can be rewritten as:
\begin{equation}
SC^{MKV} = h_{var} + \frac{1}{2} \bar{\eta}^{MKV}_0 (\mathbb{E}(\xi))^2.
\label{eq:SC_MKV_2}
\end{equation}

@@

\begin{proposition}
	Under assumption (\ref{eq:assumptions}), the difference in the social costs in the LQEMFG and LQEMKV problems can be represented by
	\begin{equation*}
		\Delta SC := SC^{MFG} - SC^{MKV} =  \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt.
	\end{equation*}
\label{prop:diff_SC}
\end{proposition}
\begin{proof}
	The solutions $\bar{\eta}^{MFG}_t$ and $\bar{\eta}^{MKV}_t$ for the Riccati equations (\ref{eq:eta_bar_MFG}) and (\ref{eq:eta_bar_MKV}), respectively, are well defined under assumption (\ref{eq:assumptions}) (see Appendix \ref{appendix_solving_fbsdes}). We notice that $\Delta\bar{\eta}_t$ defined in (\ref{eq:delta_eta}) satisfies the following first-order differential equation:
	\begin{equation*}
		\frac{d( \Delta{\bar{\eta}}_t)}{dt} = \gamma_t \Delta\bar{\eta}_t + \beta_t,
		\qquad \Delta{\bar{\eta}}_T = \lambda \bar{\eta}_T^{MFG} - \bar{\eta}_T^{MKV}
	\end{equation*}
	with coefficients:
	\begin{equation*}
	\left\{
		\begin{array}{rcl}
			\gamma_t &=& \displaystyle -2 b_1 - 2\bar{b}_1 + \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \left(\lambda \bar{\eta}_t^{MFG} + \bar{\eta}_t^{MKV} \right),\\
			\beta_t &=& \bar{b}_1 \lambda \bar{\eta}_t^{MFG} + (q + \bar{q}(1-s)^2) - \lambda (q + \bar{q}(1-s)).
		\end{array}
	\right.
	\end{equation*} 
	Since $q_T + \bar{q}_T(1-s_T) = \bar{\eta}_T^{MFG}$, $q_T + \bar{q}_T(1-s_T)^2 = \bar{\eta}_T^{MKV}$ and $\lambda \bar{\eta}_0^{MFG} - \bar{\eta}_0^{MKV} = \Delta\bar{\eta}_0$, we deduce from equations (\ref{eq:SC_MFG_2}) and (\ref{eq:SC_MKV_2}) that:
	\begin{equation*}
		\begin{split}
			& SC^{MFG} - SC^{MKV}\\
			=& \frac{1}{2} \left[ \Delta\bar{\eta}_0 (\mathbb{E}(\xi))^2 - \Delta\bar{\eta}_T (\bar{x}_T^{MFG})^2 + \int_0^T \beta_t (\bar{x}_t^{MFG})^2 dt \right] \\
			=& \frac{1}{2} \int_0^T \left[ - \frac{d (\Delta\bar{\eta}_t (\bar{x}_t^{MFG})^2) }{dt}  + \left( 	\frac{d( \Delta{\bar{\eta}}_t)}{dt} - \gamma_t \Delta\bar{\eta}_t  \right)(\bar{x}_t^{MFG})^2 \right] dt\\
			=& \frac{1}{2}\int_0^T \left[- 2\Delta{\bar{\eta}}_t \bar{x}_t^{MFG} \dot{\bar{x}}_t^{MFG} - \gamma_t \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \right]dt \\
			=& \frac{1}{2} \int_0^T \Delta{\bar{\eta}}_t (\bar{x}_t^{MFG})^2 \left[-2\left(b_1 + \bar{b}_1 - \frac{(b_2+\bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \lambda \bar{\eta}_t^{MFG}\right) - \gamma_t\right] dt\\
			=& \frac{1}{2} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt,
		\end{split}
	\end{equation*}
	where we use equation (\ref{eq:x_bar_MFG}) for the fourth equality.

@@

Therefore, under assumption (\ref{eq:assumptions}), the price of anarchy for the LQ model is given by 
\begin{equation}
PoA =1+ \frac{\Delta SC}{SC^{MKV}}= 1 +  \frac{ \displaystyle   \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1-\bar{s})^2}  \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt }{\displaystyle \int_0^T \left[q+\bar{q} + \frac{b_2^2}{r+\bar{r}} \eta_t^2 \right] v_t dt + (q_T + \bar{q}_T) v_T + \bar{\eta}_0^{MKV} (\mathbb{E}(\xi))^2}.
\label{eq:PoA_LQ}
\end{equation}\\

@@

	When $r \to \infty$ we have
	\begin{equation*}
		\lambda \to \lambda^{\infty,r} := \frac{b_2}{b_2 + \bar{b}_2}
	\end{equation*}
	and
	\begin{equation*}
		B \to 0,\ B^\eta \to 0,\ C^u \to C_u^{\infty,r} := \lambda^{\infty,r}(q + \bar{q}(1-s)),\ D^{u} \to D_u^{\infty,r} := \lambda^{\infty,r}(q_T+ \bar{q}_T(1-s_T)).
	\end{equation*}
	Since assumption (\ref{eq:assumptions}) holds for arbitrary large $r$, we can deduce that the solution $u_t$ of equation (\ref{eq:riccati_ut}) tends to a limiting function $u^{\infty,r}_t$ which is the solution of a first-order differential equation (see Appendix \ref{appendix_solving_fbsdes}). The limiting solution $u_t^{\infty,r}$ is given by:
	\begin{equation*}
	\begin{split}
	    \text{when } A^u \neq 0,\qquad & u_t^{\infty,r} = \left(D^{\infty,r}_u - \frac{C^{\infty,r}_u}{2A^u} \right) e^{-2A^u (T-t)} +  \frac{C^{\infty,r}_u}{2A^u},\\
	    \text{when } A^u = 0, \qquad & u_t^{\infty,r} = D^{\infty,r}_u + C^{\infty,r}_u (T-t),
	\end{split}
	\end{equation*}
	which is bounded for $t \in [0,T]$.
	Similarly, we have the bounded limiting solutions over $[0,T]$:
	$$w_t \xrightarrow[r \to \infty]{} w_t^{\infty,r},\qquad \eta_t \xrightarrow[r \to \infty]{} \eta_t^{\infty,r}.$$
	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, we have 
	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t
	$$
	which are also bounded over $t\in[0,T]$.
	Hence, by the bounded convergence theorem we have
	\begin{equation*}
		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty.
	\end{equation*}
	By their explicit formulas, it can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$ and therefore,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 (\mathbb{E}(\xi))^2 \  >0.
	\end{equation*}
	Thus, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we deduce $\displaystyle \lim_{r \to \infty} PoA = 1$.

@@

\begin{proof}
    First, we consider $b_2 \to 0$. If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.
    As $b_2 \to 0$, we have $\lambda \to 0 $ and
	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$
	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce
	$$u_t \xrightarrow[b_2 \to 0 ]{} 0, \quad \forall t \in [0,T].$$

	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{0,b_2,MFG}$, which is bounded over $[0,T]$.

	Since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$. Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
	\begin{equation*}
	\begin{split}
	    \text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
	    \text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
	\end{split}
	\end{equation*}
	which are bounded over $[0,T]$. Thus, the limiting variance function $ v_t \to  v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for $t>0$ and $v^{0,b_2}_t$ is bounded.
	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
	\begin{equation*}
	\begin{split}
	    \lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{0,b_2,MFG})^2 dt,\\
	    0<&\lim_{b_2 \to 0} \Delta SC < \infty,
	\end{split}
	\end{equation*}
	and using the fact that $w^{0,b_2}_t\not \equiv 0$  and using equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ (ToDo: need to justify why it is also finite!).
	Therefore, combined with equation (\ref{eq:PoA_LQ}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$
